\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instruction}}

### 2019-09-19 Documentation/Replication_Instruction.tex
tex added

\title{\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instruction}}}
\author{\normalsize\textsc{Xin Tang} \\ \normalsize\textsc{International Monetary Fund}}
\date{\normalsize\today}

@@

We use three datasets in our analysis: The National General Survey of Pollution Sources (NGSPS, \begin{CJK}{GBK}{kai}第一次全国污染源普查\end{CJK}), The National Economic Census (CNEC, \begin{CJK}{GBK}{kai}第一次全国经济普查\end{CJK}) and the Statistics of U.S. Businesses (SUSB).
\begin{itemize}
    \item
    The NGSPS is a confidential dataset housed at the Ministry of Ecology and Environment (MEE henceforth). The dataset is subject to regulation by \textit{The Law of the People's Republic of China on Guarding State Secrets} \begin{CJK}{GBK}{kai}（中华人民共和国保守国家秘密法）\end{CJK} because it contains sensitive information. Please refer to \textit{Regulation on Archiving the National General Survey of Pollution Sources Data (State Environmental Protection Administration [2007] No.187)} {\begin{CJK}{GBK}{kai}（污染源普查档案管理办法[环发[2007]187号]）\end{CJK}}. The data can only be accessed within the MEE as well as institutions under its direct supervision \begin{CJK}{GBK}{kai}（中华人民共和国生态环境部及其直属单位）\end{CJK}. Researchers affiliated with these institutions should submit application for access following the internal procedure of the MEE. This is how we access the data.

    Individual researchers not affiliated with the MEE and institutions under its direct supervision needs to submit the application through the official portal for Information Access (\begin{CJK}{GBK}{kai} 政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}. The url is retrieved on September 15th, 2019 and may vary in the future. All applications are subject to official approval by the General Office of Ministry of Ecology and Environment \begin{CJK}{GBK}{kai}（中华人民共和国生态环境部办公厅）\end{CJK}.

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} \begin{CJK}{GBK}{kai}（《污染源普查数据集》，中国环境科学出版社，2011）\end{CJK}, which is publicly available.
    \item
    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University.
    \item
    The SUSB is publicly available from the Census Bureau's dedicated website. The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

@@

We try to organize our source code by sections in the paper as much as we can. This is not always possible though (or creates unnecessary confusion). We do, however, break the code by sections within the file, where tasks that are reasonably connected logically are grouped together. The code is written such that each section is self-contained, so the readers do not have to run from the very beginning if she/he only wants to replicate a certain result. Table \ref{tab:navi_main} summarizes the correspondence between the results in the paper (tables, figures, regression results, in-text numbers, etc.) and the section of code files that computes them, as well as data dependency. To further assist the readers to visually navigate through the code, important sections are always indicated by a 76-character line of \code{=}. This is the longest line in all the source code, and should be those most visually noticeable amongst all.

>>>>

\title{\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instruction}}}
\author{
  \normalsize{{Ji Qi}} \\
  \normalsize{{Chinese Academy of Environmental Science}}
  \and
  \normalsize{{Xin Tang}}\footnote{Corresponding Author: zjutangxin@gmail.com} \\
  \normalsize{{Wuhan University}} \\
  \normalsize{{International Monetary Fund}}
  \and
  \normalsize{{Xican Xi}} \\
  \normalsize{{Fudan University}}
}
\date{\normalsize\today}

@@

We use three datasets in our analysis: The National General Survey of Pollution Sources (NGSPS, \begin{CJK}{GBK}{kai}第一次全国污染源普查\end{CJK}), The National Economic Census (CNEC, \begin{CJK}{GBK}{kai}第一次全国经济普查\end{CJK}) and the Statistics of U.S. Businesses (SUSB).
\begin{itemize}
    \item
    The NGSPS is a confidential dataset housed at the Ministry of Ecology and Environment (MEE henceforth). The dataset is subject to regulation by \textit{The Law of the People's Republic of China on Guarding State Secrets} (\begin{CJK}{GBK}{kai}中华人民共和国保守国家秘密法\end{CJK}) because it contains sensitive information. Please refer to \textit{Regulation on Archiving the National General Survey of Pollution Sources Data} (\textit{State Environmental Protection Administration [2007] No.187}, {\begin{CJK}{GBK}{kai}污染源普查档案管理办法[环发[2007]187号]\end{CJK}}). The data can only be accessed within the MEE as well as institutions under its direct supervision (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部及其直属单位\end{CJK}). Researchers affiliated with these institutions should submit application for access following the internal procedure of the MEE. This is how we access the data.

    Individual researchers not affiliated with the MEE and institutions under its direct supervision needs to submit the application through the official portal for Information Access (\begin{CJK}{GBK}{kai} 政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}. The url is retrieved on September 15th, 2019 and may vary in the future. All applications are subject to official approval by the General Office of Ministry of Ecology and Environment (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部办公厅\end{CJK}).

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.
    \item
    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University.
    \item
    The SUSB is publicly available from the Census Bureau's dedicated website. The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

@@

We try to organize our source code by sections in the paper as much as we can. This is not always possible though (or creates unnecessary confusion). We do, however, break the code by sections within the file, where tasks that are reasonably connected logically are grouped together. The code is written such that each section is self-contained, so the readers do not have to run from the very beginning if she/he only wants to replicate a certain result.\footnote{That said, the readers should always check to ensure that all the functional packages of \code{R} are loaded.} Table \ref{tab:navi_main} summarizes the correspondence between the results in the paper (tables, figures, regression results, in-text numbers, etc.) and the section of code files that computes them, as well as data dependency. To further assist the readers to visually navigate through the code, important sections are always indicated by a 76-character line of \code{=}. This is the longest line in all the source code, and should be those most visually noticeable amongst all.
